---
title: "MA 615 Refrigerator EDA Project"
author: "Shuyi Jiang, Liz Morris, Shan Shan, Luna Tang"
date: "10/10/2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load("ggplot2","knitr","dplyr")
```

# Goal of the project:
  Exploring the EIA data, we figured out that climates and regions are the least significant factors since very few homes do not use refrigerator. All of these homes are not from the coldest regions of the US, where people might not need to use refrigerator. Household income influences living condition, including housing unit type, owner/renter status and other factors. In this case, we believe that household income should be the most important factor for planning and marketing refrigerators.
  We are going to look at the type, size, age and number of refrigerators owned when the population is broken down by income.

## Part I. number of refrigerator vs household income vs household income

```{r}
use <- read.csv("use.csv", header = TRUE)
use1 <- read.csv("use1.csv", header = TRUE)
incomelevel <- c("under 20", "20 to 40", "40 to 60", "60 to 80",
                 "80 to 100", "100 to 120", "120 to 140", "140 or more")
use1$income <- factor(use1$income, levels = incomelevel)
```

## Five number summary: number of refrigerator vs household income
```{r}
summary(use)
```

## Boxplot: number of refrigerator vs household income

The boxplot indicates that around half of the families with household income of 80000 or more have more than 1 refrigerator. The majority of the richest families with household income of 140000 or more have more than 1 refrigerator.
```{r}
boxplot(use, ylab="number of refrigerator", xlab="household income")
```

## histogram: number of refrigerator vs household income

The histogram indicates the number of refrigerators own by family with different household income. All the families that do not use refrigerator have household income under 20000.
```{r}
ggplot(data = use1, aes(x= income, y = household, fill= number.of.refrigerator))+
  geom_bar(stat="identity")
```

## Summary: number of refrigerator owned by population breaking down by household income

Very limited (less than 1%) homes in the US do not have a refrigerators and they come from household with lowest income. The majority of American homes have only 1 refrigerator. As household income increases, the percentage of having more than 1 refrigerator in each income level increases. There is a jump between income levels of 60,000 to 80,000 and 80,000 to 100,000. Nearly half of homes with household income of 80,000 to 140,000 have more than 1 refrigerator. More than half of homes(54.5%) with income of 140,000 or more have at least 2 refrigerators. Thus, the second refrigerator should mainly target at homes with more than 80,000 household income.


## Part II. refrigerator size vs household income

## Five number summary: number of refrigerator size vs household income
```{r}
size2 <- read.csv("size2.csv", header = TRUE)
summary(size2)
```


## histogram: number of refrigerator vs household income
(Note: we denote the refrigerator as the first refrigerator herewith)

The histogram displays that the number of refrigerator-size owned by family varies according to household income: the higher the income, the larger the size of the refrigerator. Specifically, lower-income households, such as income under 20 thousand dollars, are more likely to "not use a refrigerator"" or use the "small size"" refrigerators; while, middle-income households would obtain the medium size refrigerators; and those with income over 140 thousand dollars prefer "very large size"" refrigerators over other sizes. Medium size refrigerators are purchased by each income groups, but be the most popular one among the lower-income groups like "20-40 thousand" and "40-60 thousand". 

```{r}
size1<-read.csv("size.csv", header=TRUE)
size <-read.csv("size.csv", header=TRUE)

incomeorder<- c('<20', '20-40', '40-60', '60-80','80-100','100-120', '120-140','>140')
sizeorder<-c('Half-size or compact','Small (less than 17.6 cubic feet)',
             'Medium (17.6 to 22.5 cubic feet)','Large (22.6 to 29.5 cubic feet)',
             'Very large (more than 29.5 cubic feet)','Do not use a refrigerator')
size1$size<- factor(size1$size, levels=sizeorder)
size1$income <- factor(size1$income, levels=incomeorder)
ggplot (data=size1, aes(x=income,y=unit,fill=size))+geom_bar(stat="identity")

```

## Summary: household income influnces the selection of refrigerator-size positively; and thus we recommend the income-oriented marketing strategy with regards to the refrigerator-size.

The study of the relationship between refrigerator-size and household income shows that different income groups have the different preferences for refrigerator-size; and the higher the income, the larger size of refrigerators. Thus, we could enhance the promotion of large size refrigerator among those high-income consumers; and also further our strategy of medium-size refrigerators among the lower-income groups. Additionally, since "very large refrigerators"" presents a promising response among the "annual income more than 140 thousand" group, we could further its market share correspondently. 

## Part III. refrigerator types vs household income

## Five number summary: refrigerator types vs household income

```{r}
type <- read.csv("type.csv") 
summary(type)
```


## Boxplot: refrigerator types vs household income
The boxplot indicates that the number of different types of refrigerator that a household owns varies as household income varies. Rich households which have larger than $80,000 income has less types of refrigerators that those with median income($20,000-$80,000). Families with less than 20,000 has the most types of refrigerators. 

```{r}
boxplot(type,xlab="income",ylab="types")
```

## histogram: refrigerator types vs household income

The histogram indicates the types of refrigerators own by families with different household income. According to the graph, two doors, top refrigerator is the most used types of families with less than 20,000 income, 20,000-40,000 income, 40,000-60,000 income, and 60,000-80,000 income. Other households use two doors, side by side refrigerators the most. Households with less than 20,000 income and households with 20,000-40,000 income has the most unites of refrigerators. 
```{r}
type1 <- read.csv("type1.csv")
ggplot(data=type1, aes(x=income, y=unites, fill=type)) + geom_bar(stat="identity")
```

## Summary: types of refrigerator owned by families breaking down by household income

Two doors, top refrigerator and two doors, side by side refrigerator are the most commonly used refrigerator types by majority of all households.Thus, marketing should be focusing on two doors, top refrigerator and two doors, side by side refrigerator. households of less than 20,000 income and households with 20,000-40,000 (median income families) have the most number of refrigerators, which indicates marketing should be focusing on these two groups of households.Half-size/compact regrigerators are only used by low income families. Companies wishing to sell half-size/compact refrigerators may focus on low income families by reducing the price of the products. 

## Part IV: Age of refrigerator vs household income

This information is useful because it shows how often people are buying refrigerators and who may be in the market for a new one. 

## Proportion Summary
```{r}
age1 <- read.csv("rg age1.csv", header = TRUE)
age <- read.csv("rg age.csv", header = TRUE)
colnames(age) <- c('Age','Under 20', '20 to 40', '40 to 60', '60 to 80',
                   '80 to 100', '100 to 120', '120 to 140', '140+')

total <- sum(age1$Units)
#aggregate(age1$Units, by=list(Category=age1$Age), FUN=sum)
age1 %>% group_by(Age) %>% summarise(proportion = sum(Units) / total)
```

This summary shows the proportions of refrigerator ages, regardless of income level. This is useful as it shows how old most people's refrigerators are.

```{r}
incomeorder <- c('Under 20', '20 to 40', '40 to 60', '60 to 80',
                 '80 to 100', '100 to 120', '120 to 140', '140+')
ageorder <- c('Less than 2 years old', '2 to 4 years old', '5 to 9 years old',
              '10 to 14 years old', '15 to 19 years old', '20 or more years old',
              'Do not use a refrigerator')

age1$Age <- factor(age1$Age, levels = ageorder)
age1$Income <- factor(age1$Income, levels=incomeorder)
```

## Boxplot

```{r}
boxplot(age[, 2:8], xlab = "Income bracket (in thousands of dollars)",
        ylab = "Units (in thousands)")
```

While this boxplot does not give much information about the ages of refrigerators, it does show which income groups have higher variations of refrigerator ages because each data point is the number of units of refrigerators in an age category.

## Bargraph

```{r}
ggplot(data=age1, aes(x=Income, y=Units, fill=Age)) +
  geom_bar(stat="identity") + 
  labs(x= "Income (in thousands of dollars)", y = "Units (in thousands)")
```

Looking at this plot, you can see that the largest number of people with new refrigerators as well as with very old refrigerators are in the lower income brackets. People with higher income have refrigerators that are between 5 and 15 years old.

## Summary
Overall, the highest proportion of people have refrigerators that are between 5 and 9 years old, suggesting that most people replace their refrigerator every 10 or so years. Additionally, we can see that the income brackets with the oldest refrigerators are the lowest ones, meaning that they may be in the market for a new refrigerator. The lowest income brackets also have higher proportions of people who have newer refrigerators, which may indicate that they buy refrigerators more often because they cannot afford to buy high quality refrigerators. Overall, it would seem that those in the lowest income brackets are most likely to be in the market for a new refrigerator and thus should be a main target of any marketing campaigns.

## Collaboration
We explored the EIA data online and shared our observations with team members. We disccused what we were interested in. And then we decided the variables we were going to look at, the method to use and the graph to interpret. Since we have 4 variables, each of us did the coding, graphing and interpreting for 1 of them. We combined our script together and finished the summary and formating together.